Presentasjon OPX Fiffig tittel

### 2022-08-03 Presentasjon/presentasjonv2.Rmd

>>>>

## <br> Phase 3 – Scrapping the scraping
- OPX wanted KPIs <br>
- Found useful KPIs <br>
- Created an interactive dashboard

## <br> Data collection & data description
- Used data from OPX and Proff.no <br>
- OPX: From their webpage. <br>
- Used to create KPIs and check our codes <br>
- Proff.no: Downloaded HTML documents. <br>
- Used to create visualizations.

# Findings

# Limitations and steps forward
